---
title: "Managing and Understanding Data"
author: "Laura Julià Melis, Víctor Navarro Garcés i Marta Piñol Palau"
date: '`r format(Sys.Date(),"%e de %B, %Y")`'
output:
  pdf_document:
    toc: yes
  html_document:
    toc: yes
bibliography: bibliography.bib
---

```{r setup, include=FALSE}
# knitr options
knitr::opts_chunk$set(echo = TRUE)

```

```{r generateBibliography, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
require("knitcitations")
cleanbib()
options("citation_format" = "pandoc")
read.bibtex(file = "bibliography.bib")
```

```{r libraries, include=FALSE}
# Install packages
# Load packages
# ...

library(knitr)
```


```{r input, include=FALSE}
# Input / Output variables
# Tuning parameters
# ...
file1 <- "usedcars.csv"

```




> * Primera toma de contacto con un informe dinámico donde se muestra algunas de sus caracteristicas.
> * Son diferentes trozos de un libro.
> * Se lee un archivo csv


-----------------------------------------------------------


`r Sys.Date()`

By the end of this notes, you will understand:

* The basic R data structures and how to use them to store and extract data

* How to get data into R from a variety of source formats
* Common methods for understanding and visualizing complex data

# R Markdown

R Markdown is an easy-to-use system that enables students to combine statistical computing in an
environment of their choosing and written analysis in one document. At a high-level, it renders
a well-annotated R script into a self-contained HTML file, replete with graphics, commands, and
stylized text.

Like LATEX or HTML, R Markdown relies on a source file and output file paradigm. Text, with simple
rules for creating styles, is typed into an R Markdown source file, which has the `.Rmd` extension. R
commands are typed directly into this file, set off in `chunks`. The `knitr` rendering engine then parses
the `.Rmd` file. It first executes each of the R commands in the `chunks` and processes the output from
those commands. This generates an intermediate Markdown file (with a `.md` extension) which is of
no immediate interest. Next, it renders this Markdown file into a single HTML file with embedded
graphics. 


This information is from [@baumer2014r]

# R data structures

The R data structures used most frequently in machine learning are *vectors*, *lists*, 
and *data frames*.


## Vectors 

The fundamental R data structure is the **vector**, which stores an ordered set of
values called **elements**. A vector can contain any number of elements. However, all
the elements must be of the same type; for instance, a vector cannot contain both
numbers and text.

There are several vector types commonly used in machine learning:`integer`(numbers without decimals), `numeric` (numbers with decimals), `character` (text data),
or `logical` (`TRUE` or `FALSE` values). There are also two special values: `NULL`, which is
used to indicate the absence of any value, and `NA`, which indicates a missing value.

More information [@lantz2015machine, pp. 28-30]


## Data Frames 

Data frames are the preferred way for organizing data sets that are of modest size. Fpr now, think of data grames as a rectangurlar row by column layout, where the rows are observations and the columns are variables.

This information is from  [@maindonald2006data, p. 4] For More information [@maindonald2006data , section: 1.4 subsection: 1.2]

## Lists

Like vectors, lists are ordered sequences of elements, but unlike vectors, the elements of a list can themselces have more than one element. Thus we can have lists of vectors, lists of data frames, or lists containing a mixture of numbers, strings, vectors, data frames and other lists. 

Lists are created with the `list()` function.

This information is from  [@baayen2008analyzing, p. 16]



Create vectors of data for three medical patients:

```{r chunck1}
# create vectors of data for three medical patients
subject_name <- c("John Doe", "Jane Doe", "Steve Graves")
temperature <- c(98.1, 98.6, 101.4)
flu_status <- c(FALSE, FALSE, TRUE)
```



Access the second element in body temperature vector:

```{r chunck2}
# access the second element in body temperature vector
temperature[2]
```

Examples of accessing items in vector include items in the range 2 to 3.

```{r chunck3}
## examples of accessing items in vector
# include items in the range 2 to 3
temperature[2:3]
```


Exclude item 2 using the minus sign
```{r chunck4}
# exclude item 2 using the minus sign
temperature[-2]

```



Use a vector to indicate whether to include item

```{r chunk 5}
# use a vector to indicate whether to include item
temperature[c(TRUE, TRUE, FALSE)]

```



# Exploring and understanding data

After collecting data and loading it into R data structures, the next step in the
machine learning process involves examining the data in detail. It is during this
step that you will begin to explore the data's features and examples, and realize the
peculiarities that make your data unique. The better you understand your data, the
better you will be able to match a machine learning model to your learning problem.
The best way to understand the process of data exploration is by example. In this
section, we will explore the *`r file1`*  dataset, which contains actual data about
used cars recently advertised for sale on a popular U.S. website.

...

...

...


Since the dataset is stored in CSV form, we can use the `read.csv()` function to load
the data into an R data frame:

```{r read}
##### Exploring and understanding data --------------------

## data exploration example using used car data
usedcars <- read.csv(file1, stringsAsFactors = FALSE)

```



## Exploring the structure of data
One of the first questions to ask in your investigation should be about how data
is organized. If you are fortunate, your source will provide a **data dictionary**, a
document that describes the data's features. In our case, the used car data does not
come with this documentation, so we'll need to create our own.


```{r str}
# get structure of used car data
str(usedcars)

```

## Show some registers


```{r table1}
# Table of 6 first registers
kable(head(usedcars))

```


## Exploring numeric variables


```{r explore}
## Exploring numeric variables -----

# summarize numeric variables
summary(usedcars$year)
summary(usedcars[c("price", "mileage")])

# calculate the mean income
(36000 + 44000 + 56000) / 3
mean(c(36000, 44000, 56000))

# the median income
median(c(36000, 44000, 56000))

# the min/max of used car prices
range(usedcars$price)

# the difference of the range
diff(range(usedcars$price))

# IQR for used car prices
IQR(usedcars$price)

# use quantile to calculate five-number summary
quantile(usedcars$price)

# the 99th percentile
quantile(usedcars$price, probs = c(0.01, 0.99))

# quintiles
quantile(usedcars$price, seq(from = 0, to = 1, by = 0.20))
```


## Visualizing numeric variables - boxplots

```{r graphics1, fig.asp=0.6,  fig.caption="test"}
# boxplot of used car prices and mileage
boxplot(usedcars$price, main="Boxplot of Used Car Prices",ylab="Price ($)")

```


```{r graphics2, fig.height = 3, fig.width = 5, fig.caption="test"}
boxplot(usedcars$mileage, main="Boxplot of Used Car Mileage",
      ylab="Odometer (mi.)")

```



```{r graphics3, fig.height = 4, fig.width = 6, fig.align = "center"}
# histograms of used car prices and mileage
hist(usedcars$price, main = "Histogram of Used Car Prices",
     xlab = "Price ($)")

```

```{r graphics4, fig.width = 5, fig.asp = .62}
hist(usedcars$mileage, main = "Histogram of Used Car Mileage",
     xlab = "Odometer (mi.)")

```

```{r descriptive}
# variance and standard deviation of the used car data
var(usedcars$price)
sd(usedcars$price)
var(usedcars$mileage)
sd(usedcars$mileage)

```



## Measuring spread - quartiles and the five-number summary


The **five-number summary** is a set of five statistics that roughly depict the spread
of a dataset. All five of the statistics are included in the output of the `summary()`
function. Written in order, they are:

1. Minimum (`Min.`)
2. First quartile, or Q1 (`1st Qu.`)
3. Median, or Q2 (`Median`)
4. Third quartile, or Q3 (`3rd Qu.`)
5. Maximum (`Max.`)

## Measuring spread - variance and standard deviation

In order to calculate the standard deviation, we must first obtain the **variance**, which
is defined as the average of the squared differences between each value and the
mean value. In mathematical notation, the variance of a set of `n` values of `x` is defined
by the following formula. The Greek letter `mu` ($\mu$) (similar in appearance to an m)
denotes the mean of the values, and the variance itself is denoted by the Greek letter
`sigma` ($\sigma$) squared (similar to a b turned sideways):

$$
Var(X)= \sigma^2 = \frac{1}{n}\sum_{i=1}^n (x_i - \mu)^2
$$


The standard deviation is the square root of the variance, and is denoted by `sigma` as
shown in the following formula:

$$
StdDev(X)= \sigma = \sqrt{\frac{1}{n}\sum_{i=1}^n (x_i - \mu)^2}
$$



# Chunk that shows several graphics together.

```{r}
par(mfrow=c(2,2))
plot(usedcars$year,usedcars$price,xlab='Year', ylab='Price', main= 'Bond Price and Year', pch=16, col='red')
boxplot(price~color,data=usedcars, main= 'Boxplot of Price', col=rainbow(11))
hist(usedcars$mileage, col='orange', main='Histogram of mileage', xlab='Mileage')
barplot(table(usedcars$model), col=heat.colors(3), main='Frequencies chart of model')
```

# Chunk that shows a data table

```{r}
kable(cor(usedcars[,c(1,3,4)]), caption='A data table: Correlation between Year, Price and Mileage.', align= 'c')
```

*Note*. For more details on using mathematical expressions in Latex (R Markdown) see <https://es.sharelatex.com/learn/Mathematical_expressions>.

